\blue{...Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios...}

### 2017-07-12 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

\medskip
In this section, two numerical simulations were conducted with fixed and adaptive mesh resolutions to qualitatively assess model capability to capture fingers dynamics (\ie formation and growth). In order to trigger the formation of fingers, regions with sharp synthetic permeability gradient were introduced. The computational domain, Fig.~\ref{fig:testcase_heter_domain} (a), consists of a rectangular domain dully saturated with five regions with prescribed permeabilities, and

>>>>

\medskip
In this section, two numerical simulations were conducted with fixed and adaptive mesh resolutions to qualitatively assess model capability to capture fingers dynamics (\ie formation and growth). In order to trigger the formation of fingers, regions with sharp synthetic permeability gradient were introduced. The computational space, Fig.~\ref{fig:testcase_heter_domain} (a), consists of a rectangular domain fully saturated with a fluid (except by a squared region containing 50$\%$ of a second fluid -- wetting fluid phase) and divided into 5 regions with prescribed permeabilities. No-flux boundary conditions were imposed on the upper and lower borders, whilst pure wetting fluid phase $\left(\text{\ie} S_{1}=1\right)$ is driven into the domain from the left-hand face at $u_{1}=1$.
